Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

The lower row in Figure \ref{fig:cumulative_alignment} shows the
alignments with the halo in the MHD simulations. 
This time the halo shape changes and twists at different radii.
However around the radius of $0.25R_{200}$ there is an alignment
almost perfect between the shapes of the stellar disc and the dark
matter halo. 
Above and below this radius there are halos with a lower degree of
alignment.
Across the three different alignments we measure we verify that the
strongest one is indeed the one between the two minor axis.

Statistically the strongest missalignment is found with the halo shape
at a radius of $R_{200}/16\sim (14\pm1)$ kpc. 
At this radius the mean angle and its standard deviation between the
two minor axis is $18 \pm 21$ degrees, with one extreme case
(\texttt{Au-4}) where the angle is close to $78$ degrees. 
In contrast at $0.25 R_{200}$ the angle between the two axis is
$2\pm 3$ degrees without any extreme outlier.

>>>>

The upper row in Figure \ref{fig:cumulative_alignment} shows 
the alignments between the major/intermediate/minor axis of the
disk and the halo as a function of the dimensionless radius at which
the halo shape was measured.
The upper row shows the angle between the DMO halo and the stellar
disk in the MHD simulation.
This comparison help us to measure how the shape directions in the
dark matter shells change with radius.
For the bulk of the sample the lines are horizontal.
Only two halos in the sample show a significant change in alignment in
on the three shape axis.

The lower row in Figure \ref{fig:cumulative_alignment} shows th
results for the MHD simulations.
The most striking feature of this plot is that around the radius of
$0.25R_{200}$ there is an almost perfect halo-disc alignment measured
in three shape axis.
Above and below this radius the degree of alignment changes.
We find the strongest missalignments at a radius of $0.06R_{200}$ when
the median and the standard deviation of the alignment angles between
the minor/median/major axis are $18\pm18$, $25\pm22$ and $7\pm21$
degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
$2\pm4$ an $1\pm 3$ degrees, respectively

This changing alignment as a function of radius can be seen as a
twisting in the shape ellipsoids. 
As we are dealing with oblate halos $b/a\approx 1$ and the
directions corresponding to the medium and major axis could be subject
to noise.
For this reason, in order to better quantify the twisting for each
halo we take the standard deviation of the angle between the two minor
axis, which should be less succeptible to noise.
With this measurement, twisting becomes a global property of the halo,
as the standard deviation is measured over the different radii at
which we have quantified the alignment.

Figure \ref{fig:alignment_correlations} shows the correlation between
twisting at the four different radii at which we have measured the
alignments.
